\subsubsection{ILC}

\begin{tabularx}{\textwidth}{l | X}
  Period & Details \\
  \hline
  2004 & Decision to use super conducting technology was made. \\
  2005 & The Global Design Effort completed a baseline design for the ILC. \\
  2007 & A more detailed Reference Design Report (RDR) was published, which provides a technical and detailed description of the project and includes an initial value estimate. \\
  2013 & The Technical Design Phase (TDP) produced technical design of the project, in order to demonstrate its feasibility to all involved governments. \\
  2015 & The host country is to be expected to be chosen at a meeting of leaders from participating countries of ILC. \\
  2016\textendash 26 & Construction of ILC is estimated to take 10 years. \\
\end{tabularx}
    
\subsubsection{CLIC}

\begin{tabularx}{\textwidth}{l | X}
    Period & Details \\
    \hline 
    2012 & CLIC Conceptual Design Report was finalised and feasibility was established. \\
    2012\textendash 16 & Project development phase intended to produce a Project Implementation Plan (PIP) for CLIC construction. \\
    2016\textendash 17 & Decision about the next project at the energy frontier. \\
    2017\textendash 22 & Project Implementation Phase, including an initial Project Preparation Phase to lay the groundwork for construction. \\
    2022\textendash 23 & CLIC construction setup. \\
    2023\textendash 30 & Construction of energy stage, making use of the hardware developed during the Project Implementation Phase. \\
    2030+ & Commissioning of CLIC. \\
\end{tabularx}